### 2022-11-28 abstract.tex
paper 2
Maria feedback

The fact that a scientific finding can be replicated in an independent
replication study is central for its credibility. However, various large-scale
replication failures have shown that the replicability of scientific findings is
often lower than expected. This ``replication crisis'' has led to several
methodological reforms in the past decade, an increased conduct of replication
studies being one of them. Yet despite this rise of replication research, there
is no consensus on which statistical methods should be used for the design and
analysis of replication studies; Various methods already exist and various new
ones have been proposed in response to the crisis. This thesis centres around
the proposal from \citet{Held2020}, which is based on a reverse-Bayes approach.
The key idea is to reverse the traditional ``forward'' use of Bayes' theorem
(``prior + likelihood $\rightarrow$ posterior''), starting instead with a
pre-specified posterior and deducing the corresponding prior (``posterior +
likelihood $\rightarrow$
prior''). % As such, the reverse-Bayes approach naturally fits to the replication
% setting as it enables the mathematical formalization of scepticism regarding the
% finding from the original study.
This allows to challenge the original finding by determining a sceptical prior
for the underlying effect size such that the resulting posterior is no longer
convincing. This prior then represents the position of a sceptic who remains
unconvinced by the original study. Whether or not the sceptics' position is
justified can then be assessed in light of the new data from the replication
study. The larger the conflict between the replication data and the sceptic, the
larger the degree of replication success. This procedure can be summarized in a
single quantitative measure of replication success, termed the sceptical
$p$-value.

The first and largest part of the thesis consists of extending this procedure. A
first extension replaces tail probabilities by Bayes factors as measures of
evidence. The sceptical prior is now determined such that the original finding
is no longer convincing in terms of a Bayes factor. In contrast to tail
probabilities, Bayes factors have a more natural interpretation and allow for
direct quantification of evidence for one hypothesis versus another. Similarly
as with the sceptical $p$-value, the procedure leads to a single measure
quantifying the degree of replication success called the sceptical Bayes factor.
A second extensions recalibrates the original procedure to produce more
appropriate inferences in terms of effect size. % from the relative effect size
% perspective
The recalibration is chosen such that for borderline significant original
studies, replication success can only be achieved if the replication effect
estimate is larger than the original one. The third extension provides a
framework for Bayesian design of replication studies. The framework allows
combining the data from the original study with external knowledge, which leads
to potentially more efficient designs compared to classical approaches.

>>>>

The fact that a scientific finding can be replicated in an independent
replication study is central to its credibility. However, various large-scale
replication failures have shown that the replicability of scientific findings is
often lower than expected. This ``replication crisis'' has led to several
methodological reforms in the past decade, an increased conduct of replication
studies being one of them. Yet despite this rise of replication research, there
is no consensus on which statistical methods should be used for the design and
analysis of replication studies; Various methods already exist and various new
ones have been proposed in response to the crisis. This thesis centres around a
proposal based on the reverse-Bayes approach. The key idea is to reverse the
traditional ``forward'' use of Bayes' theorem (``prior + likelihood
$\rightarrow$ posterior''), starting instead with a pre-specified posterior and
deducing the corresponding prior (``posterior + likelihood $\rightarrow$
prior''). % As such, the reverse-Bayes approach naturally fits to the replication
% setting as it enables the mathematical formalization of scepticism regarding the
% finding from the original study.
This allows us to challenge the original finding by determining a sceptical
prior for the underlying effect size such that the resulting posterior is no
longer convincing. This prior then represents the position of a sceptic who
remains unconvinced by the original study. Whether or not the sceptics' position
is justified can then be assessed in light of the new data from the replication
study. The larger the conflict between the replication data and the sceptic, the
larger the degree of replication success. This procedure can be summarized in a
single quantitative measure of replication success, termed the sceptical
$p$-value.

The first and largest part of the thesis consists of extending this procedure. A
first extension replaces tail probabilities by Bayes factors as measures of
evidence. The sceptical prior is now determined such that the original finding
is no longer convincing in terms of a Bayes factor. In contrast to tail
probabilities, Bayes factors have a more natural interpretation and allow for
direct quantification of evidence for one hypothesis versus another. As with the
sceptical $p$-value, the procedure leads to a single measure quantifying the
degree of replication success called the sceptical Bayes factor. A second
extensions recalibrates the original procedure to produce more appropriate
inferences in terms of effect size. % from the relative effect size
% perspective
The recalibration is chosen such that for borderline significant original
studies, replication success can only be achieved if the replication effect
estimate is larger than the original one. The third extension provides a
framework for Bayesian design of replication studies. This framework allows for
combining the data from the original study with external knowledge, which leads
to potentially more efficient designs compared to classical approaches.
